# Analysis Results
 
```{r setup , include=FALSE}
library(MASS)
library(dplyr)
library(tidyverse)
library(knitr)
```

```{r, include=FALSE}
strike.reports <- read.csv("C:/Users/crack/Desktop/Proseminar/strike reports.csv")
resize <- strike.reports %>% filter((SIZE %in% c('Large','Medium','Small')))
glm1 <- glm(INDICATED_DAMAGE ~ SIZE, data = resize, family=binomial)
summary(glm1)
confint(glm1)
## odds ratios only
exp(coef(glm1))
## odds ratios and 95% CI
exp(cbind(OR = coef(glm1), confint(glm1)))
# create odds ratios
o1 <- as_tibble(round(exp(coef(summary(glm1))[,1]),3))
# create CIs
c1 <- as_tibble(round(exp(confint(glm1)), 3))
# rename columns
c1 <- c1 %>% rename(lb = `2.5 %`,
                    ub = `97.5 %`)
```

```{r, include=FALSE}
strike.reports <- read.csv("C:/Users/crack/Desktop/Proseminar/strike reports.csv")
warned1 <- strike.reports %>% filter(WARNED %in% c('No', 'Yes'))
glm2 <- glm(INDICATED_DAMAGE ~ WARNED, data = warned1, family=binomial)
summary(glm2)
## odds ratios and 95% CI
exp(cbind(OR = coef(glm2), confint(glm2)))
# create odds ratios
o2 <- as_tibble(round(exp(coef(summary(glm2))[,1]),3))
# create CIs
c2 <- as_tibble(round(exp(confint(glm2)), 3))
# rename columns
c2 <- c2 %>% rename(lb = `2.5 %`,
                    ub = `97.5 %`)
```

```{r, include=FALSE}
strike.reports <- read.csv("C:/Users/crack/Desktop/Proseminar/strike reports.csv")
glm3 <- glm(INDICATED_DAMAGE ~ INGESTED, data = strike.reports, family=binomial)
summary(glm3)
## odds ratios and 95% CI
exp(cbind(OR = coef(glm3), confint(glm3)))
# create odds ratios
o3 <- as_tibble(round(exp(coef(summary(glm3))[,1]),3))
# create CIs
c3 <- as_tibble(round(exp(confint(glm3)), 3))
# rename columns
c3 <- c3 %>% rename(lb = `2.5 %`,
                    ub = `97.5 %`)
```

### INDICATED DAMAGE

#### Unadjusted Associations

The estimated models can be written as:

\[ \text{logit} \left({\pi} \right) = `r round(coef(summary(glm1))[,1][1], 2)`  `r round(coef(summary(glm1))[,1][3], 2)` \text{Small} `r round(coef(summary(glm1))[,1][2], 2)` \text{Medium} \]

\[ \text{logit} \left({\pi} \right) = `r round(coef(summary(glm2))[,1][1], 2)`  `r round(coef(summary(glm2))[,1][2], 2)` \text{Warned} \]

\[ \text{logit} \left({\pi} \right) = `r round(coef(summary(glm3))[,1][1], 2)` + `r round(coef(summary(glm3))[,1][2], 2)` \text{Ingested} \]

#### Undjusted associations: Odds Ratios

| Predictor | Odds Ratios | (95% CI)  |  *p*-value |
|---|---|---|---|
| Size: Small  | `r o1$value[3]` | (`r c1$lb[3]`, `r c1$ub[3]`)  |  < 0.001  |
| Size: Medium |  `r o1$value[2]` | (`r c1$lb[2]`, `r c1$ub[2]`)  | < 0.001   |
| Size: Large | reference | |
| Warned: Yes  | `r o2$value[2]` | (`r c2$lb[2]`,`r c2$ub[2]`)  |  < 0.001  |
| Warned: No | reference | |
| Ingested: Yes  | `r o3$value[2]` | (`r c3$lb[2]`,`r c3$ub[2]`)  |  < 0.001  |
| Ingested: No | reference | |

Small birds' odds of damaging the aircraft are `r o1$value[3]` times that of large birds. Medium birds' odds of damaging the aircraft are `r o1$value[2]` times that of large birds. The odds of damaging the aircraft when the pilot is warned are `r o2$value[2]` times that of not being warned. The odds of damaging the aircraft when a bird is ingested are `r o3$value[2]` times that of not being ingested.

<br>

#### Adjusted associations: Indicated Damage ~ Size + Warned + Ingested

```{r, include=FALSE}
strike.reports <- read.csv("C:/Users/crack/Desktop/Proseminar/strike reports.csv")
resize <- strike.reports %>% filter((SIZE %in% c('Large','Medium','Small')),(WARNED %in% c('No', 'Yes')))
glm11 <- glm(INDICATED_DAMAGE ~ SIZE+WARNED+INGESTED, data = resize, family=binomial)
summary(glm11)
confint(glm11)
## odds ratios only
exp(coef(glm11))
## odds ratios and 95% CI
exp(cbind(OR = coef(glm11), confint(glm11)))
# create odds ratios
o11 <- as_tibble(round(exp(coef(summary(glm11))[,1]),3))
# create CIs
c1 <- as_tibble(round(exp(confint(glm11)), 3))
# rename columns
c1 <- c1 %>% rename(lb = `2.5 %`,
                    ub = `97.5 %`)
```

The estimated model can be written as:

\[ \text{logit} \left({\pi} \right) = `r round(coef(summary(glm11))[,1][1], 2)`  `r round(coef(summary(glm11))[,1][3], 2)` {\text{Small}} `r round(coef(summary(glm11))[,1][2], 2)` {\text{Medium}} `r round(coef(summary(glm11))[,1][4], 2)` \text{Warned} + `r round(coef(summary(glm11))[,1][5], 2)` \text{Ingested} \]

#### Adjusted associations: Odds Ratios

| Predictor | Odds Ratios | (95% CI)  |  *p*-value |
|---|---|---|---|
| Size: Small  | `r o11$value[3]` | (`r c1$lb[3]`, `r c1$ub[3]`) |  < 0.001  |
| Size: Medium |  `r o11$value[2]` | (`r c1$lb[2]`, `r c1$ub[2]`) | < 0.001   |
| Size: Large | reference | |
| Warned: Yes  | `r o11$value[4]` | (`r c1$lb[4]`, `r c1$ub[4]`) |  < 0.001  |
| Warned: No | reference | |
| Ingested: Yes  | `r o11$value[5]` | (`r c1$lb[5]`, `r c1$ub[5]`) |  < 0.001  |
| Ingested: No | reference | |

Small birds' odds of damaging the aircraft are `r o11$value[3]` times that of large birds. Medium birds' odds of damaging the aircraft are `r o11$value[2]` times that of large birds. The odds of damaging the aircraft when the pilot is warned are `r o11$value[4]` times that of not being warned. The odds of damaging the aircraft when a bird is ingested are `r o11$value[5]` times that of not being ingested.

```{r, include=FALSE}
strike.reports <- read.csv("C:/Users/crack/Desktop/Proseminar/strike reports.csv")
size4 <- strike.reports %>% filter((DAMAGE_LEVEL %in% c('D', 'M', 'M?', 'N', 'S')),(TIME_OF_DAY %in% c('Dawn', 'Day', 'Dusk', 'Night')))
size4$DAMAGE_LEVEL = as.factor(size4$DAMAGE_LEVEL)
size4$TIME_OF_DAY = as.factor(size4$TIME_OF_DAY)
is.factor(size4$TIME_OF_DAY)
table(size4$TIME_OF_DAY)
m5 <- polr(DAMAGE_LEVEL ~ TIME_OF_DAY, data = size4, Hess=TRUE)
summary(m5)
# store table
(ctable <- coef(summary(m5)))
# calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
#combined table
(ctable1 <- (cbind(ctable, "p value" = p)))
## OR and CI
(ci <- confint(m5))
exp(cbind(OR = coef(m5), ci))
c5 <- round(exp(cbind(OR = coef(m5), ci)),3)

```

```{r, include=FALSE}
strike.reports <- read.csv("C:/Users/crack/Desktop/Proseminar/strike reports.csv")
size5 <- strike.reports %>% filter((DAMAGE_LEVEL %in% c('D', 'M', 'M?', 'N', 'S')),(SKY %in% c('No Cloud', 'Overcast', 'Some Cloud')))
size5$DAMAGE_LEVEL = as.factor(size5$DAMAGE_LEVEL)
size5$SKY = as.factor(size5$SKY)
is.factor(size5$SKY)
table(size5$SKY)
m4 <- polr(DAMAGE_LEVEL ~ SKY, data = size5, Hess=TRUE)
summary(m4)
## store table
(ctable <- coef(summary(m4)))
## calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
#combined table
(ctable2 <- cbind(ctable, "p value" = p))
## profiled CIs
(ci <- confint(m4)) 
## odds ratios
exp(coef(m4))
## OR and CI
exp(cbind(OR = coef(m4), ci))
c4 <- round(exp(cbind(OR = coef(m4), ci)),3)
```

```{r, include=FALSE}
strike.reports <- read.csv("C:/Users/crack/Desktop/Proseminar/strike reports.csv")
size1 <- strike.reports %>% filter((SIZE %in% c('Large','Medium','Small')),
                                   (DAMAGE_LEVEL %in% c('D', 'M', 'M?', 'N', 'S')))
size1$DAMAGE_LEVEL = as.factor(size1$DAMAGE_LEVEL)
is.factor(size1$DAMAGE_LEVEL)
m8 <- polr(DAMAGE_LEVEL ~ SIZE, data = size1, Hess=TRUE)
summary(m8)
# store table
ctable <- coef(summary(m8))
# calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
#combined table
(ctable4 <- cbind(ctable, "p value" = p))

## OR and CI
(ci <- confint(m8))
exp(cbind(OR = coef(m8), ci))
# create odds ratios
o8 <- as_tibble(round(exp(coef(summary(m8))[,1]),3))
# create CIs
c8 <- as_tibble(round(exp(confint(m8)), 3))
# rename columns
c8 <- c8 %>% rename(lb = `2.5 %`,
                    ub = `97.5 %`)
```

```{r, include=FALSE}
strike.reports <- read.csv("C:/Users/crack/Desktop/Proseminar/strike reports.csv")
size2 <- strike.reports %>% filter((WARNED %in% c('No', 'Yes')),
                                   (DAMAGE_LEVEL %in% c('D', 'M', 'M?', 'N', 'S')))
size2$DAMAGE_LEVEL = as.factor(size2$DAMAGE_LEVEL)
size2$DAMAGE_WARNED = as.factor(size2$WARNED)
m <- polr(DAMAGE_LEVEL ~ WARNED, data = size2, Hess=TRUE)
summary(m)
# store table
(ctable <- coef(summary(m)))
# calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
#combined table
(ctable5 <- (cbind(ctable, "p value" = p)))
## OR and CI
(ci <- confint(m))
exp(cbind(OR = coef(m), t(ci)))
c6 <- round(exp(cbind(OR = coef(m), t(ci))),3)
# create odds ratios
o7 <- as_tibble(round(exp(coef(summary(m))[,1]),3))
# create CIs
c7 <- as_tibble(round(exp(confint(m)), 3))
```

```{r, include=FALSE}
strike.reports <- read.csv("C:/Users/crack/Desktop/Proseminar/strike reports.csv")
size3 <- strike.reports %>% filter((DAMAGE_LEVEL %in% c('D', 'M', 'M?', 'N', 'S')))
size3$DAMAGE_LEVEL = as.factor(size3$DAMAGE_LEVEL)
m6 <- polr(DAMAGE_LEVEL ~ INGESTED, data = size3, Hess=TRUE)
summary(m6)
# store table
(ctable <- coef(summary(m6)))
# calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
#combined table
(ctable3 <- (cbind(ctable, "p value" = p)))
## OR and CI
(ci <- confint(m6))
exp(cbind(OR = coef(m6), t(ci)))
c16 <- round(exp(cbind(OR = coef(m6), t(ci))),3)
# create odds ratios
o6 <- as_tibble(round(exp(coef(summary(m6))[,1]),3))
```

### DAMAGE LEVEL

#### Undjusted associations: Damage Level*

The estimated models can be written as:

|Logit$\hat{P}(Y \le j)$ | Intercept | Day | Dusk | Night |
|---|---|---|---|---|
|Logit$\hat{P}(Y \le 1)$|`r round(ctable1[4],2)`|`r round(ctable1[1],2)`|`r round(ctable1[2],2)`|`r round(ctable1[3],2)`|
|Logit$\hat{P}(Y \le 2)$|`r round(ctable1[5],2)`|`r round(ctable1[1],2)`|`r round(ctable1[2],2)`|`r round(ctable1[3],2)`|
|Logit$\hat{P}(Y \le 3)$|`r round(ctable1[6],2)`|`r round(ctable1[1],2)`|`r round(ctable1[2],2)`|`r round(ctable1[3],2)`|
|Logit$\hat{P}(Y \le 4)$|`r round(ctable1[7],2)`|`r round(ctable1[1],2)`|`r round(ctable1[2],2)`|`r round(ctable1[3],2)`|
      
|Logit$\hat{P}(Y \le j)$ | Intercept |Overcast | SomeClouds |
|---|---|---|---|
|Logit$\hat{P}(Y \le 1)$|`r round(ctable2[3],2)`|`r round(ctable2[1],2)`|`r round(ctable2[2],2)`|
|Logit$\hat{P}(Y \le 2)$|`r round(ctable2[4],2)`|`r round(ctable2[1],2)`|`r round(ctable2[2],2)`|
|Logit$\hat{P}(Y \le 3)$| `r round(ctable2[5],2)`|`r round(ctable2[1],2)`|`r round(ctable2[2],2)`|
|Logit$\hat{P}(Y \le 4)$|`r round(ctable2[6],2)`|`r round(ctable2[1],2)`|`r round(ctable2[2],2)`|

|Logit$\hat{P}(Y \le j)$| Intercept | Small| Medium |
|---|---|---|---|
|Logit$\hat{P}(Y \le 1)$|`r round(ctable4[3],2)`|`r round(ctable4[2],2)`|`r round(ctable4[1],2)`|
|Logit$\hat{P}(Y \le 2)$|`r round(ctable4[4],2)`|`r round(ctable4[2],2)`|`r round(ctable4[1],2)`|
|Logit$\hat{P}(Y \le 3)$|`r round(ctable4[5],2)`|`r round(ctable4[2],2)`|`r round(ctable4[1],2)`|
|Logit$\hat{P}(Y \le 4)$|`r round(ctable4[6],2)`|`r round(ctable4[2],2)`|`r round(ctable4[1],2)`|

|Logit$\hat{P}(Y \le j)$ | Intercept | Warned|
|---|---|---|
|Logit$\hat{P}(Y \le 1)$|`r round(ctable5[2],2)`|`r round(ctable5[1],2)`|
|Logit$\hat{P}(Y \le 2)$|`r round(ctable5[3],2)`|`r round(ctable5[1],2)`|
|Logit$\hat{P}(Y \le 3)$|`r round(ctable5[4],2)`|`r round(ctable5[1],2)`|
|Logit$\hat{P}(Y \le 4)$|`r round(ctable5[5],2)`|`r round(ctable5[1],2)`|

|Logit$\hat{P}(Y \le j)$ | Intercept | Ingested|
|---|---|---|
|Logit$\hat{P}(Y \le 1)$|`r round(ctable3[2],2)`|`r round(ctable2[1],2)`|
|Logit$\hat{P}(Y \le 2)$|`r round(ctable3[3],2)`|`r round(ctable2[1],2)`|
|Logit$\hat{P}(Y \le 3)$|`r round(ctable3[4],2)`|`r round(ctable2[1],2)`|
|Logit$\hat{P}(Y \le 4)$|`r round(ctable3[5],2)`|`r round(ctable2[1],2)`|

#### Undjusted associations: Odds Ratios

| Predictor | Odds Ratios | (95% CI)  |  *p*-value |
|---|---|---|---|
| Time of Day: Day | `r c5[1]`, (`r c5[4]`,`r c5[7]`)  | < 0.001 |
| Time of Day: Dusk | `r c5[2]`, (`r c5[5]`,`r c5[8]`) |  < 0.001 |
| Time of Day: Night | `r c5[3]`, (`r c5[6]`,`r c5[9]`) |  < 0.001  |
| Time of Day: Dawn | reference |  |
| Sky: Overcast | `r c4[1]`, (`r c4[3]`,`r c4[5]`) | < 0.05 |
| Sky: Some Clouds | `r c4[2]`, (`r c4[4]`,`r c4[6]`) |  < 0.001  |
| Sky: No Clouds | reference | |
| Size: Small  |  `r o8$value[1]`  (`r c8$lb[1]`, `r c8$ub[1]`)  |  < 0.001  |
| Size: Medium |  `r o8$value[2]`  (`r c8$lb[2]`, `r c8$ub[2]`)  | < 0.001   |
| Size: Large | reference | |
| Warned: Yes | `r c6[1]`, (`r c6[2]`,`r c6[3]`)  |  < 0.001  |
| Warned: No  | reference | |
| Ingested: Yes | `r c16[1]`, (`r c16[2]`,`r c16[3]`)  |  < 0.001  |
| Ingested: No  | reference | |

The odds of damaging the aircraft during the day are `r c5[1]` times that of during dawn. The odds of damaging the aircraft during dusk are `r c5[2]` times that of during dawn. The odds of damaging the aircraft during the night are `r c5[3]` times that of during dawn. The odds of damaging the aircraft with overcast skies are `r c4[1]` times that of no clouds. The odds of damaging the aircraft with some clouds in the sky are `r c5[2]` times that of no clouds. Small birds' odds of damaging the aircraft are  `r o8$value[1]` times that of large birds. Medium birds' odds of damaging the aircraft are `r o8$value[2]` times that of large birds. The odds of damaging the aircraft when the pilot is warned are `r c6[1]` times that of not being warned. The odds of damaging the aircraft when a bird is ingested are `r c16[1]` times that of not being ingested.

<br>

#### Adjusted Associations Model: Damage Level

```{r, include=FALSE}
strike.reports <- read.csv("C:/Users/crack/Desktop/Proseminar/strike reports.csv")
size4 <- strike.reports %>% filter((DAMAGE_LEVEL %in% c('D', 'M', 'M?', 'N', 'S')),(TIME_OF_DAY %in% c('Dawn', 'Day', 'Dusk', 'Night')),(SKY %in% c('No Cloud', 'Overcast', 'Some Cloud')),(SIZE %in% c('Large','Medium','Small')),(WARNED %in% c('No', 'Yes')))
size4$DAMAGE_LEVEL = as.factor(size4$DAMAGE_LEVEL)
size4$TIME_OF_DAY = as.factor(size4$TIME_OF_DAY)
is.factor(size4$TIME_OF_DAY)
size4$SKY = as.factor(size4$SKY)
is.factor(size4$SKY)
size4$DAMAGE_WARNED = as.factor(size4$WARNED)
m5 <- polr(DAMAGE_LEVEL ~ TIME_OF_DAY + INGESTED + SIZE + WARNED + SKY, data = size4, Hess=TRUE)
summary(m5)
# store table
(ctable <- coef(summary(m5)))
# calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
#combined table
(ctable1 <- (cbind(ctable, "p value" = p)))
## OR and CI
(ci <- confint(m5))
exp(cbind(OR = coef(m5), ci))
c1 <- round(exp(cbind(OR = coef(m5), ci)),3)

```


| Intercept | Day | Dusk | Night | Ingested | Small | Medium | Warned | Overcast | Some Clouds |
|---|---|---|---|---|---|---|---|---|
|`r round(ctable1[10],2)`|`r round(ctable1[1],2)`|`r round(ctable1[2],2)`|`r round(ctable1[3],2)`|`r round(ctable1[4],2)`|`r round(ctable1[5],2)`|`r round(ctable1[6],2)`|`r round(ctable1[7],2)`|`r round(ctable1[8],2)`| `round(ctable1[8],2)`|
|`r round(ctable1[11],2)`|`r round(ctable1[1],2)`|`r round(ctable1[2],2)`|`r round(ctable1[3],2)`|`r round(ctable1[4],2)`|`r round(ctable1[5],2)`|`r round(ctable1[6],2)`|`r round(ctable1[7],2)`|`r round(ctable1[8],2)`| `round(ctable1[8],2)`|
|`r round(ctable1[12],2)`|`r round(ctable1[1],2)`|`r round(ctable1[2],2)`|`r round(ctable1[3],2)`|`r round(ctable1[4],2)`|`r round(ctable1[5],2)`|`r round(ctable1[6],2)`|`r round(ctable1[7],2)`|`r round(ctable1[8],2)`| `round(ctable1[8],2)`|
|`r round(ctable1[13],2)`|`r round(ctable1[1],2)`|`r round(ctable1[2],2)`|`r round(ctable1[3],2)`|`r round(ctable1[4],2)`|`r round(ctable1[5],2)`|`r round(ctable1[6],2)`|`r round(ctable1[7],2)`|`r round(ctable1[8],2)`| `round(ctable1[8],2)`|


```{r, include=FALSE}
strike.reports <- read.csv("C:/Users/crack/Desktop/Proseminar/strike reports.csv")
size4 <- strike.reports %>% filter((DAMAGE_LEVEL %in% c('D', 'M', 'M?', 'N', 'S')),(TIME_OF_DAY %in% c('Dawn', 'Day', 'Dusk', 'Night')),(SKY %in% c('No Cloud', 'Overcast', 'Some Cloud')),(SIZE %in% c('Large','Medium','Small')),(WARNED %in% c('No', 'Yes')))
size4$DAMAGE_LEVEL = as.factor(size4$DAMAGE_LEVEL)
size4$TIME_OF_DAY = as.factor(size4$TIME_OF_DAY)
is.factor(size4$TIME_OF_DAY)
size4$SKY = as.factor(size4$SKY)
is.factor(size4$SKY)
size4$DAMAGE_WARNED = as.factor(size4$WARNED)
m5 <- polr(DAMAGE_LEVEL ~ TIME_OF_DAY + INGESTED + SIZE + WARNED + SKY, data = size4, Hess=TRUE)
summary(m5)
# store table
(ctable <- coef(summary(m5)))
# calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
#combined table
(ctable1 <- (cbind(ctable, "p value" = p)))
## OR and CI
(ci <- confint(m5))
exp(cbind(OR = coef(m5), ci))
c1 <- round(exp(cbind(OR = coef(m5), ci)),3)

```

#### Adjusted associations: Odds Ratios 

| Predictor | Odds Ratios | (95% CI)  |  *p*-value |
|---|---|---|---|
| TIME OF DAY: Day | `r c1[1]` | (`r c1[10]`,`r c1[19]`)  | < 0.001 |
| TIME OF DAY: Dusk | `r c1[2]`| (`r c1[11]`,`r c1[20]`) |  < 0.001 |
| TIME OF DAY: Night | `r c1[3]` | (`r c1[12]`,`r c1[21]`) |  < 0.001  |
| Ingested: Yes | `r c1[4]` | (`r c1[13]`,`r c1[22]`)  |  < 0.001  |
| Size: Small  |  `r c1[6]` | (`r c1[15]`,`r c1[23]`)  |  < 0.001  |
| Size: Medium |  `r c1[5]` | (`r c1[14]`,`r c1[24]`)  | < 0.001   |
| Warned: Yes | `r c1[7]` | (`r c1[16]`,`r c1[25]`)  |  < 0.001  |
| Sky: Overcast | `r c1[8]` | (`r c1[17]`,`r c1[26]`) | < 0.05 |
| Sky: Some Clouds | `r c1[9]` | (`r c1[18]`,`r c1[27]`) |  < 0.001  |

#### Adjusted associations:  Damage Level*

```{r, include=FALSE}
strike.reports <- read.csv("C:/Users/crack/Desktop/Proseminar/strike reports.csv")
size4 <- strike.reports %>% filter((DAMAGE_LEVEL %in% c('D', 'M', 'M?', 'N', 'S')),(TIME_OF_DAY %in% c('Dawn', 'Day', 'Dusk', 'Night')),(SKY %in% c('No Cloud', 'Overcast', 'Some Cloud')),(SIZE %in% c('Large','Medium','Small')),(WARNED %in% c('No', 'Yes')))
size4$DAMAGE_LEVEL = as.factor(size4$DAMAGE_LEVEL)
size4$TIME_OF_DAY = as.factor(size4$TIME_OF_DAY)
is.factor(size4$TIME_OF_DAY)
size4$SKY = as.factor(size4$SKY)
is.factor(size4$SKY)
size4$DAMAGE_WARNED = as.factor(size4$WARNED)
m5 <- polr(DAMAGE_LEVEL ~ TIME_OF_DAY + INGESTED + SIZE + WARNED + SKY, data = size4, Hess=TRUE)
summary(m5)
# store table
(ctable <- coef(summary(m5)))
# calculate and store p values
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
#combined table
(ctable1 <- (cbind(ctable, "p value" = p)))
## OR and CI
(ci <- confint(m5))
exp(cbind(OR = coef(m5), ci))
c1 <- round(exp(cbind(OR = coef(m5), ci)),3)

```


The odds of damaging the aircraft during the day are `r c1[1]` times that of during dawn. The odds of damaging the aircraft during dusk are `r c1[2]` times that of during dawn. The odds of damaging the aircraft during the night are `r c1[3]` times that of during dawn. The odds of damaging the aircraft when a bird is ingested are `r c1[4]` times that of not being not being ingested. Small birds' odds of damaging the aircraft are  `r c1[6]` times that of large birds. Medium birds' odds of damaging the aircraft are `r c1[5]` times that of large birds. The odds of damaging the aircraft when the pilot is warned are `r c1[7]` times that of not being warned. The odds of damaging the aircraft with overcast skies are `r c1[8]` times that of no clouds. The odds of damaging the aircraft with some clouds in the sky are `r c1[9]` times that of no clouds.

